Weather covariance matrices as U_hyp for GR50

### 2021-02-09 R/Analysis_v0.6_QTL_interval_plotting.Rmd
Make figures for Tom's DOE talk 2021

>>>>

```{r}
	Chr06N_41610882
plot_df <- mash_plot_effects(m_midw_fl_hyp, i = 41793)

ggb1 <- plot_df$effect_df %>%
    mutate(Pos_plot = plot_df$marker,
           subpop = "Midwest") %>%
    mutate(Conditions = str_remove(Conditions, "Gulf_and_Midwest_")) %>%
  mutate(Conditions = str_remove(Conditions, "Gulf_")) %>%
  mutate(Conditions = str_remove(Conditions, "Midwest_")) %>%
  separate(Conditions, into = c("Phenotype", "Garden"), sep = -3) %>%
  mutate(Phenotype = str_remove(Phenotype, "_$"),
         Garden = str_remove(Garden, "^_")) %>%
  mutate(Garden = str_replace(Garden, "0_M", "MI"),
         Phenotype = str_replace(Phenotype, "FL5$", "FL50"))
ggb1$Garden <- factor(ggb1$Garden, levels = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD"))

  ggb1 %>%
  ggplot() + 
  geom_point(mapping = aes(x = Garden, y = .data$mn)) +
  switchgrassGWAS::theme_oeco +
  geom_errorbar(mapping = aes(ymin = .data$mn - .data$se,
                              ymax = .data$mn + .data$se,
                              x = Garden), width = 0.3) +
  geom_hline(yintercept = 0, lty = 2) +
  facet_wrap(~Pos_plot+subpop, nrow = 1) +
  labs(x = "", y = "Effect Size (% total variation)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  coord_flip()

  ave_plot(filename = "../manuscript/plots/Figure_DOE_mash_SNP_effects.png", plot = last_plot(), base_height = 2.4, base_width = 2)
```

### 2021-02-09 R/Analysis_v0.6_weather_covariance_Uhyp_greenup.Rmd
Make figures for Tom's DOE talk 2021

### iii. Plot setup
Make a list containing all of the ggplots for all entries in the covariance grid represented by `pw_df`.
Then view all the ggplots in gglist.
```{r mashhattan plots loop}
pw_df <- pw_gg

gglist <- list()
log10BF <- expression(paste("log"[10], plain("(Bayes Factor)")))
for(i in seq_along(names(pw_df)[-(1:5)])){
  var <- names(pw_df)[i+4]  
  gglist[[i]] <- pw_df %>%
    arrange(!! sym(var)) %>%
    ggplot(aes(x = .data$Pos, y = .data$log10BayesFactor)) +
    switchgrassGWAS::theme_oeco +
    geom_point(aes(color = !! sym(var), fill = !! sym(var),
                   shape = as.factor(.data$Chr))) +
    facet_wrap(~ .data$Chr, nrow = 1, scales = "free_x", 
               strip.position = "bottom") +
    scale_color_viridis_c(option = "D", end = 0.95) + 
    scale_fill_viridis_c(option = "D", end = 0.95) +
    theme(strip.text = element_text(size = 8),
          axis.text.y = element_text(size = 8),
          axis.text.x = element_blank(),
          legend.text = element_text(size = 8),
          axis.ticks.x = element_blank(),
          panel.background = element_rect(fill=NA)) +
    labs(x = "Chromosome", y = log10BF) +
    scale_x_continuous(expand = c(0.32, 0.32)) +
    scale_shape_manual(values = rep(c(21,22),9), guide = FALSE) +
    geom_hline(yintercept = 2, linetype = 2) +
    ggtitle(var)
}
gglist
```

@@

>>>>

### iii. Plot setup
Make a list containing all of the ggplots for all entries in the covariance grid represented by `pw_df`.
Then view all the ggplots in gglist.
```{r mashhattan plots loop}
pw_df <- pw_mf

gglist <- list()
log10BF <- expression(paste("log"[10], plain("(Bayes Factor)")))
for(i in seq_along(names(pw_df)[-(1:5)])){
  var <- names(pw_df)[i+4]  
  gglist[[i]] <- pw_df %>%
    arrange(!! sym(var)) %>%
    filter(!! sym(var) > 0.01) %>%
    ggplot(aes(x = .data$Pos, y = .data$log10BayesFactor)) +
    switchgrassGWAS::theme_oeco +
    geom_point(aes(color = !! sym(var), fill = !! sym(var),
                   shape = as.factor(.data$Chr))) +
    facet_wrap(~ .data$Chr, nrow = 1, scales = "free_x", 
               strip.position = "bottom") +
    scale_color_viridis_c(option = "D", end = 0.95) + 
    scale_fill_viridis_c(option = "D", end = 0.95) +
    theme(strip.text = element_text(size = 8),
          axis.text.y = element_text(size = 8),
          axis.text.x = element_blank(),
          legend.text = element_text(size = 8),
          axis.ticks.x = element_blank(),
          panel.background = element_rect(fill=NA)) +
    labs(x = "Chromosome", y = log10BF) +
    scale_x_continuous(expand = c(0.32, 0.32)) +
    scale_shape_manual(values = rep(c(21,22),9), guide = FALSE) +
    geom_hline(yintercept = 2, linetype = 2) +
    ggtitle(var)
}
ggdoe1 <- gglist[[6]] + ggtitle("SNPs in the Midwest subpopulation that covary strongly with cumulative GDD")
save_plot(filename = "../manuscript/plots/Mashhattan_covar_Midwest_flowering_cgdd.png", base_width = 9, plot = ggdoe1)
ggdoe2 <- gglist[[9]] + ggtitle("SNPs in the Midwest subpopulation with equal effects at all gardens")
save_plot(filename = "../manuscript/plots/Mashhattan_covar_Midwest_flowering_equal_effects.png", base_width = 9, plot = ggdoe2)
```

@@

Chr06N_41610882
mash_plot_effects(m_midw_fl_hyp, i = 41793)
```
Not many SNPs with U_hyp loading > 10% and SNP with log10BF > 2:
Both GR: 10 & 9 SNPs   cgdd_12c_18d_Gulf_and_Midwest x2 (0.9 and 0.10)
Both FL: 2 SNPs        dyln_change_sec_Midwest.7
